---
title: "STAT F611 Homework 01"
author: "Henry Agbi-Kaiser"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2: 
              highlight:   
              toc: false
              latex_engine: xelatex
              extra_dependencies: ["geometry"]
              citation_package: natbib
geometry: legalpaper, left=1in, right=1in, top=1in, bottom=1in

header-includes:
  - \usepackage{changepage}
  - \usepackage{subcaption}
---


```{r, echo=FALSE, warning=FALSE, include=FALSE }
library(TSA)
library(ggplot2)
```

\textbf{1.1} 
The scatterplot of LA rainfall versus last year’s LA rainfall is presented in Figure \@ref(fig:sp-of-LA).

\begin{figure}[htbp]
    \centering
        \includegraphics[width=0.5\textwidth]{plots/scatterplot_of_LA.pdf}
    \caption{Scatterplot of LA Rainfall versus Last Year’s LA Rainfall}
    \label{fig:sp-of-LA}
\end{figure}
 
\textbf{Code}
```{r, eval=FALSE}
data(larain)
data<-data.frame(y=larain, x=zlag(larain))
p.larain <- ggplot(data = data, mapping = aes(x,y))+
  geom_point()+
  theme_bw()+
  xlab("Previous Year Inches")+
  ylab("Inches")
```

\vspace{1cm}
\textbf{1.2} 
The time series plot of color property from a chemical process is presented in Figure \@ref(fig:tsp-color-property).

\begin{figure}[htbp]
    \centering
        \includegraphics[width=0.7\textwidth]{plots/tsp_color_property.pdf}
    \caption{Time Series Plot of Color Property from a Chemical Process}
    \label{fig:tsp-color-property}
\end{figure}


\textbf{Code}
```{r, eval=FALSE}
data(color)
data<-data.frame(y=color, x= c(1:length(color)))
p.color <- ggplot(data = data, mapping = aes(x,y))+
  geom_line()+
  geom_point()+
  theme_bw()+
  xlab("Batch")+
  ylab("Color Property")
```

\newpage
\textbf{1.5}
Three time series plots of 48 random t-distributed values (df = 5) are presented in Figure \@ref(fig:tsp-t). All three plots look "random" since the values appear to fluctuate without any pattern and they look nonnormal.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/tsp-t-1.pdf}
        \subcaption{Random Sample 1}
        \label{fig:normal4}
    \end{subfigure}
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/tsp-t-2.pdf}
         \subcaption{Random Sample 2}
    \end{subfigure}
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/tsp-t-3.pdf}
         \subcaption{Random Sample 3}
    \end{subfigure}
    \caption{Time Series Plots of 48 Random t-Distributed Values (df = 5)}
    \label{fig:tsp-t}
\end{figure}

\textbf{Code}
```{r, eval=FALSE}
n <- 48
df <- 5
tdata <- rt(n, df)
data <- data.frame(y=tdata, x= c(1:length(tdata)))
p.t <- ggplot(data = data, mapping = aes(x,y))+
  geom_line()+
  geom_point()+
  theme_bw()+
  xlab("Time")+
  ylab("Value")
```

\vspace{1cm}
\textbf{1.6}
The time series plot of the average monthly temperatures of Dubuque, Iowa is presented in Figure \@ref(fig:tsp-average).

\begin{figure}[htbp]
    \centering
        \includegraphics[width=0.7\textwidth]{plots/tsp-average.pdf}
    \caption{Time Series Plot of Average Monthly Temperatures, Dubuque, Iowa}
    \label{fig:tsp-average}
\end{figure}

\textbf{Code}
```{r, eval=FALSE}
data(tempdub)
data<-data.frame(y=tempdub, x=time(tempdub), s=as.vector(substr(season(tempdub),1,1)))
p.temdub <- ggplot(data = data, mapping = aes(x,y))+
  geom_line()+
  geom_text(aes(label=s))+
  theme_bw()+
  xlab("Time")+
  ylab("Temperature")
```

